Missing years 2019 and 2020^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-04-24 outputs/paper/paper.Rmd
grammer edited (1)

# Introduction
Although we are currently heading back to life before COVID-19, it is no exaggeration to say that COVID-19 has altered substantial portions of life style especially until end of 2021. For instance, remote work or wearing masks in public spaces has become usual. Of course, many of us feel uncomfortable about the strict sanctions. Then, my question was who should be in charge of this pandemic. Speaking of results, it should be all of us. Probably, without radical advances in technology, such virus would not exist. However, blaming each of us for the pandemic is very rare, rather many of us tend to blame government for lack of professional actions. Then, which fields  are more vulnerable to criticism? This brings me to write this paper.

This paper is going to explore changes in U.S citizen opinions on government spending levels before and after COVID-19. Following that, I have obtained U.S GSS 2018 and 2021, and sorted variables that I considered as potential variables changed during the pandemic. Since I aimed to figure out government spending on various fields, I mainly extracted national spending levels as the variables. However, there remains a clear gap that needs to be filled. Because this paper is about general thoughts changes on government spending levels, it was hard to make decisions that some changes were due to the pandemic or not. For instance, 26% of participants said national spending on arms was too much in 2018, and 32% of them said it was too much in 2021. It is hard to tell whether the increase is solely due to the pandemic or not.

In order to discern the changes by the pandemic, I was required to research U.S society backgrounds in 2018 and 2021, and they were used to along with data analysis. By plotting graphs for comparison, I sorted responses as three factors: Positive, Negative and unchanged. For instance, for positive response, many of participants required more national budgets on welfare. 
In general, national spending on public service such as education earned positive. On the other hand, national spending on arms, or foreign aids earned negative. Of course, there exists exceptions, and they are going to be dealt with in result and discussion session.

This paper is important in a sense that it can present new plans and visions for government budgets. Also, in a broader sense, other countries can refer to this paper for simple comparison. 
Before we jump into the main session, I am going to briefly introduce you remained index of this paper, and what they are about.

@@

4) Results: you are going to read summary and analysis of data.

5) Discussion: what is remained to be solved.

@@

For this paper, I aimed to find out changes in U.S citizens' minds regarding the government before and after COVID-19 outbreak. Following that, I obtained datasets from U.S GSS 2018 and 2021 considering first outbreak of COVID-19, which was in Dec 2019. Dataset collected through US GSS is aimed for the goal that enabling the cleanest comparison to show changes in public opinion in the United States. Usually, it is conducted in person, however because of pandemic, this time it was conducted via online. There are numerous surveys about COVID-19, however in order to observe general thought changes, they are not as appropriate as U.S GSS. Most COVID-19 surveys were specifically aimed for healthcare fields. For instance, whether healthcare system was enough to cover all patients or not was a major point for most COVID-19 surveys. On the other hand, U.S GSS datasets included more various fields such as national spending on drug, crime and etc, thus it can rather represent more general changes than specific areas.
Among countless variables existing in U.S GSS, I chose national spending levels and government actions. Since I needed to use two different years for comparison, I had to extract variables that were in common, then combined them. Also, since number of samples was different, converting sample size to percentage was needed.

@@

First, to make the demarcation between data session and appendix, I focused on two parts: whether there existed different patterns and noticeable changes between two graphs 2018 and 2021. For instance, figure \@ref(fig:fig7) shows us same pattern between 2018 and 2022, and there exists subtle changes. On the other hand, although figure \@ref(fig:fig6) presents the same pattern, changes in percentage are relatively fluctuating than others. For an another example, figure \@ref(fig:fig2) presents different pattern between 2018 and 2021. Therefore, with respect to the two aspects, I am going to explain my data here.

@@

This two variables are very similar. Income equality is regarding whether government should impose more taxes on the rich for better income equality or not, and help poor is whether government should be responsible for helping the poor or not. Thankfully, they both present similar pattern, which enhances the reliability about the survey. Majority thinks that government and individuals both are responsible for income differences. One thing to notice here is that voice for government responsibility increased over years.

@@

The two graph in figure \@ref(fig:fig19) seems very similar, but this does not mean that it does not possess valuable meanings. In 2020 - 2021 when U.S GSS 2021 was conducted, although COVID-19 cases did not surge up as much as 2022, but with eyes in 2021, it was increasing. However, before and after COVID-19, there is no difference in response regarding government actions toward the sick. Majority think that more actions needed toward the sick from the government

@@

Since I do not have exact y-value in my data, I am going to create representative from three categories: positive, negative and unchanged, then double check whether they belong to appropriate groups or not. To do that, I am going to create a multiple linear regression model. Since changes must move together once they belong to same groups, I decided that multiple linear regression model can explain better than others. In order to sort variables into the three groups, I followed the result from data session, and set changes less than 5% as unchanged. The outcome is as followed:

1) Positive: Drug Addicts, Welfare

@@

3) Unchanged: Childcare, Crime rates, Education, Energy, Environment, Mass Transportation, Park and recreation, Roads, Scientific research, Social security

4) Government responsibility : helppoor, helpsick, eqwlth

natheal, natsci, natroad, natenrgy and natcrime appeared in the corresponding models insignificant. However, this does not mean that I needed to re-arrange the groups, rather it shows that there is no linear relations with chosen y- value. Also, since different changes in percentage is evident, they must belong to original groups, and further interpretation is going to be made in result and discussion session.

```{r, include = FALSE}
d_data <- rbind(reduced_data1, reduced_data2)
model1 <- lm(natfare ~ natdrug, data = d_data)
model2 <- lm(nataid ~ natarms + natcity  + natrace + natheal, data = d_data )
model3 <- lm(natchld ~ natcrime + nateduc + natenrgy + natenvir + natmass + natpark + natroad + natsci + natsoc, data = d_data)
model4 <- lm(helppoor ~  helpsick + eqwlth, data = d_data)
```

@@

First, let's take a look at the positive group. This also includes government responsibility group excluding helppoor as they both present voices on more government actions needed. Following that, figure \@ref(fig:fig6), figure \@ref(fig:fig10), figure \@ref(fig:fig20), and figure \@ref(fig:fig21) belong to this group. One interesting result is national spending levels on drug figure \@ref(fig:fig6). According to CDC, death from overdoes in U.S is increasing over years, but the fact that respondents moved to "About right" on the national spending level contradicts with the CDC data, although majority of them answered "Too little", 70% in 2018 and 61% in 2021. Unlike small increase in drug overdoes death in other years, it noticeably increased during the pandemic. The movement conveys an important message here: indifference. During the pandemic, especially between 2020 and 2021, there was strict lock down policy in U.S. Other than essential workers, most had to stay at home, which caused for people to be indifferent about their surroundings. 
In addition to the indifference from the lock down, it also brought financial problems. People who could work remote was rare comparing to people who could not. In other words, there was serious layoffs although government gave financial aids. This naturally caused many to consider more actions and funds were needed, which appeared in welfare (figure \@ref(fig:fig10)), helppoor (figure \@ref(fig:fig20)) and eqwlth (figure \@ref(fig:fig21)).

Second, let's explore into the negative group: Figure \@ref(fig:fig1), Figure \@ref(fig:fig2), Figure \@ref(fig:fig4), Figure \@ref(fig:fig11), and Figure \@ref(fig:fig14).
They all show increase in "Too much". There were few things that were showed very interesting results. One was health part. It is true that majority answered "Too little" for national spending on healthcare in both years. However, it dropped by 5.8%. Although this is little above from the standard of change I set in the model session, and it did not solely fit into the group, considering 2020 survey was conducted during the pandemic, it was surprising. According to Forbes, critical care beds per capita in U.S is the highest In other words, unlike other countries, U.S was comparatively able to handle serious patients well. Also, as the pandemic went on, the virus got weaker, which enabled people to treat themselves at home. I suspect that this is why there was drop in "Too little". Therefore, health must stay in the negative group. In addition to the health part, race presented very interesting result as well. Black Lives Matter was a big issue during 2020,however, voice for more actions dropped over the years. It is absolutely true that there should not be any discrimination against races. However, violence cannot be justified under the name of equality. After George Floyd was murdered by a police officer in May 25, 2020, serious riots and looting occurred all over U.S. I think the drop in "Too little" was appeared as a counteraction of the violence. The rest variables make sense if you think of the pandemic situation. During the pandemic, not only vaccines were more needed than guns, but taking care of own nation came first than helping other countries. Therefore, it is natural to observe the negative in arms, foreign aids and big city problems.

Last is the unchanged group:  Figure \@ref(fig:fig3), Figure \@ref(fig:fig5), Figure \@ref(fig:fig7), Figure \@ref(fig:fig8), Figure \@ref(fig:fig9), Figure \@ref(fig:fig12), Figure \@ref(fig:fig13), Figure \@ref(fig:fig15), Figure \@ref(fig:fig16) and Figure \@ref(fig:fig17).
This group can be interpreted as a group that is absolutely essential in society. For instance, no matter what we face, education 
1. Essential
2. Indifference regarding the virus.

@@

# Appendix {-}
In this session, I am going to deal with remained data explanation. Since no dramatic changes were observed in remained variables, I combined them by patterns.

>>>>

# Introduction
Although we are currently heading back to the life before COVID-19, it is no exaggeration to say that COVID-19 has altered substantial portions of life style. For instance, remote work or wearing masks in public spaces has become usual. Of course, many of us feel uncomfortable about the strict sanctions. Then, my question was who should be in charge of this pandemic. Speaking of the result, it should be all of us. Probably, without radical advances in technology, such virus would not exist. However, situation of blaming each of us for the pandemic is very rare, rather many of us tend to blame government for lack of professional actions. Then, which fields are more vulnerable to criticism? This brings me to write this paper.

This paper is going to explore changes in U.S citizen opinions on government spending levels before and after COVID-19. Following that, I have obtained data from U.S GSS 2018 and 2021, and sorted variables that I considered as potential variables that were possibly changed during the pandemic. I aimed to figure out government spending on various fields, so I mainly extracted national spending levels as the variables. However, there remains a clear gap that needs to be filled. Because this paper is about general thought changes on government spending levels, it was hard to make clear decisions that the changes were due to solely the pandemic or not. For instance, 26% of participants said national spending on arms was too much in 2018, and 32% of them said it was too much in 2021. It is hard to tell whether the increase was occurred solely from the pandemic or not.

In order to discern the changes by the pandemic and others, I was required to research U.S society backgrounds from 2018 to 2021, and they were used along with data analysis. By plotting graphs for comparison between 2018 and 2021, I was able to sort the variables o=into three categories: Positive, Negative and unchanged reaction. For instance, for the positive reaction, there was drop in "Too much" and increase in "Too little" and vice versa for negative category. National spending on welfare and drug belong to the positive group. On the other hand, national spending on arms, or foreign aids belong to negative. Of course, there exists exceptions within the groups, and they are going to be dealt with in result and discussion session.

This paper is important in a sense that the pandemic is not over yet, so it can present new plans and visions for government budgets. Also, in a broader sense, other countries can refer to this paper for simple comparison. 
Before we jump into the main session, I am going to briefly introduce you remained index of this paper, and what they are about.

@@

4) Results: you are going to read summary and interpretation of data.

5) Discussion: you are going to read reamined questions and weakness.

@@

For this paper, I aimed to find out changes in U.S citizens' minds regarding the government before and after COVID-19 outbreak. Following that, I obtained datasets from U.S GSS 2018 and 2021 considering the first outbreak of COVID-19, which was in Dec 2019. Dataset collected through US GSS is aimed for the goal that enabling the cleanest comparison to show changes in public opinion in the United States. Usually, it is conducted in person, however because of pandemic, this time it was conducted via online. There are numerous surveys regarding COVID-19, however in order to observe general thought changes, they are not as appropriate as U.S GSS since most COVID-19 surveys were specifically aimed for healthcare fields. For instance, whether healthcare system was enough to cover all patients or not was a major point for most COVID-19 surveys. On the other hand, U.S GSS datasets included more various fields such as national spending on drug, crime and etc, thus it enabled to represent more general changes.
Among countless variables existing in U.S GSS, I chose national spending levels and government actions. Since I needed to use two different years for comparison, I had to extract variables that were in common, then combined them. Also, since number of samples was different, converting sample size to percentage was needed.

@@

First, to make the demarcation between data session and appendix, I focused on two parts: whether there existed different patterns or noticeable changes between two graphs 2018 and 2021. For instance, figure \@ref(fig:fig7) shows us same pattern between 2018 and 2022, and there exists subtle changes. On the other hand, although figure \@ref(fig:fig6) presents the same pattern, but changes in percentage are relatively fluctuating than others. For an another example, figure \@ref(fig:fig2) presents different pattern between 2018 and 2021. Therefore, with respect to the two aspects, I am going to explain my data here.

@@

This two variables are very similar. Income equality was regarding whether government should impose more taxes on the rich for better income equality or not, and help poor was whether government should be responsible for helping the poor or not. Thankfully, they both presented similar pattern, which enhanced the reliability about the survey. Majority thought that government and individuals both were responsible for income differences. One thing to notice here was that voice for government responsibility increased over years.

@@

The two graph in figure \@ref(fig:fig19) seems very similar, but this does not mean that it does not possess valuable meanings. In 2020 - 2021 when U.S GSS 2021 was conducted, although COVID-19 cases did not surge up as much as 2022, but with eyes in 2021, it was increasing. However, there was no difference in response regarding government actions toward the sick. Majority thought that more actions needed toward the sick from the government

@@

Since I do not have exact y-value in my data, I am going to create representative from the three categories: positive, negative and unchanged, then double check whether they belong to appropriate groups or not. To do that, I am going to use multiple linear regression model. Since changes must move together once they belong to same groups, I decided that multiple linear regression model could explain better than others. In order to sort variables into the three groups, I followed the result from data session, and set changes less than 5% as unchanged. The outcome is as followed:

1) Positive: Drug Addicts, Welfare, eqwlth, helppoor

@@

3) Unchanged: Childcare, Crime rates, Education, Energy, Environment, Mass Transportation, Park and recreation, Roads, Scientific research, Social security, helpsick

natheal, natsci, natroad, and natpark appeared in the corresponding models insignificant. However, this does not mean that I needed to re-arrange the groups, rather it shows that there was no linear relations with chosen y- value. Also, since different changes in percentage is evident, they must belong to original groups, and further interpretation is going to be made regarding this in result and discussion session.

```{r, include = FALSE}
d_data <- rbind(reduced_data1, reduced_data2)
model1 <- lm(natfare ~ natdrug + eqwlth + helppoor , data = d_data)
model2 <- lm(nataid ~ natarms + natcity  + natrace + natheal, data = d_data )
model3 <- lm(helpsick ~ natchld + natcrime + nateduc + natenrgy + natenvir + natmass + natpark + natroad + natsci + natsoc, data = d_data)
summary(model3)
```

@@

First, let's take a look at the positive group. Following that, figure \@ref(fig:fig6), figure \@ref(fig:fig10), figure \@ref(fig:fig20), and figure \@ref(fig:fig21) belong to this group. One interesting result is that national spending levels on drug figure \@ref(fig:fig6). According to CDC, death from overdoes in U.S is increasing over years, but the fact that respondents moved to "About right" on the national spending level contradicts with the CDC data, although majority of them answered "Too little", 70% in 2018 and 61% in 2021. Unlike small increase in drug overdoes death in other years, it noticeably increased during the pandemic. The movement conveys an important message here: indifference. During the pandemic, especially between 2020 and 2021, there was strict lock down policy in U.S. Other than essential workers, most had to stay at home, which I assumed to cause for people to be indifferent about their surroundings. 
In addition to the indifference from the lock down, the lock down also brought financial problems. People who could work remote was rare comparing to people who could not. In other words, there was serious layoffs although government gave financial aids. This naturally caused many to consider more actions and funds needed, which appeared in welfare (figure \@ref(fig:fig10)), helppoor (figure \@ref(fig:fig20)) and eqwlth (figure \@ref(fig:fig21)).

Second, let's explore into the negative group: Figure \@ref(fig:fig1), Figure \@ref(fig:fig2), Figure \@ref(fig:fig4), Figure \@ref(fig:fig11), and Figure \@ref(fig:fig14).
They all show increase in "Too much". There were few things that presented very interesting results. One was health part. It is true that majority answered "Too little" for national spending on healthcare in both years. However, it dropped by 5.8%. Although this is little above from the standard of change I set in the model session, and the variable did not fit into the group, considering 2020 when the survey was conducted, it was surprising. According to Forbes, critical care beds per capita in U.S is the highest among many countries. In other words, unlike other countries, U.S was comparatively able to handle serious patients well. Also, as the pandemic went on, the virus got weaker, which enabled people to treat themselves at home. I suspect that this is why there was drop in "Too little". Therefore, health must stay in the negative group. In addition to the health part, race presented very interesting result as well. Black Lives Matter was a big issue during 2020, however, voice for more actions dropped over the years. It is absolutely true that there should not be any discrimination against races. However, violence cannot be justified under the name of equality. After George Floyd was murdered by a police officer in May 25, 2020, serious riots and looting occurred all over U.S. I think the drop in "Too little" was occured as a counteraction of the violence. The rest variables make sense if you think of the pandemic situation. During the pandemic, not only vaccines were more needed than guns, but taking care of own nation came first than helping other countries. Therefore, it is natural to observe the negative in arms, foreign aids and big city problems.

Last is the unchanged group:  Figure \@ref(fig:fig3), Figure \@ref(fig:fig5), Figure \@ref(fig:fig7), Figure \@ref(fig:fig8), Figure \@ref(fig:fig9), Figure \@ref(fig:fig12), Figure \@ref(fig:fig13), Figure \@ref(fig:fig15), Figure \@ref(fig:fig16) and Figure \@ref(fig:fig17).
This group can be interpreted as a group that was absolutely essential in society regardless the virus. For instance, no matter what we face, education must go on. In a same sense, other variables must go on regardless the virus. One thing to notice here is the outdoor services such as mass transportation, park or roads. One of major changes before and after the pandemic is virtual life. Many facilities ran virtually, so I assumed that national spending on outdoor services would belong to the negative group. However, it turned out to be unchanged. This means that they jumped clear of the pandemic.

@@

# Appendix {-}
In this session, I am going to deal with remained data explanation. Since no noticeable changes were observed in remained variables, I combined them by patterns.
